Expected Dependency Pair Match: Predicting translation quality with expected syntactic structure

### 2009-08-10 mtjournal.tex
Mari's changes to introduction

Machine translation (MT) evaluation is a challenge for research
because the space of good translations is large, and two equally good
translations may appear to be quite different at first glance. 
%
The challenges of choosing among translations are compounded when this
evaluation is done automatically.
%
Human evaluation, however, is both time-consuming and difficult, so
research has turned increasingly towards automatic measures of
translation quality, usually by comparing the system (hypothesis) translation to
one or more reference (human) translations.
%
Automatic measures of this kind not
only provide a well-defined evaluation standard but are also required
for training on error criteria, e.g.\ with minimum error rate training
\cite{och03mert}.

Currently, the most popular evaluation measures include a measure
based on $n$-gram precision known as BLEU \cite{papineni02bleu} and
the edit-distance measure Translation Edit Rate (TER)
\cite{snover06ter}.  Recent research has found that these measures may
not accurately track translation quality both empirically
\cite{charniak03syntaxlmmt} and theoretically
\cite{callisonburch06bleuproblems}.

These challenges have motivated a search for better measures that
incorporate additional language knowledge sources.  METEOR
\cite{banerjee05meteor}, for example, uses synonym tables and
morphological stemming to do progressively more-forgiving matching.
It can be tuned towards recall or precision, but is generally not
tuned by users.  TER Plus (TERp) \cite{snover09terp} is an extension of the
previously-mentioned TER that also incorporates synonym sets and stemming, along
with automatically-derived paraphrase tables.  TERp is explicitly
intended to be tuned to a development set by users.
%
Tuning has the advantage that the weight of different types of errors
can be adjusted to match the needs of the task, though it makes it
more difficult to compare results across tasks, particularly when
there is little data for tuning.

As an alternative to these synonym- and paraphrase-based approaches,
other metrics model syntactically-local (rather than string-local)
word-sequences. \inlinecite{liu05syntaxformteval} compared tree-local
$n$-gram precision in various configurations of constituency and
dependency trees.  The dependency-based SParseval measure
\cite{roark06:sparseval}, designed as a parse-quality metric for
speech, is a similar approach, in that it is an F-measure over a
decomposition of reference and hypothesis trees.
\inlinecite{owczarzak07evaluatingmt} proposed \textbf{d} and
\textbf{d\_var} measures that compare relational tuples derived from a
lexical functional grammar (LFG)
over reference and hypothesis translations and reported substantial
improvement in correlation with human judgment relative to BLEU and
TER.

These syntactically-oriented measures require a system for proposing
dependency structure over the reference and hypothesis
translations. Some \cite{liu05syntaxformteval,roark06:sparseval} use
PCFG parsers with deterministic head-finding, while others
\cite{owczarzak07evaluatingmt} extract the semantic dependency
relations from an LFG parser \cite{cahill04lfg}.
%
This work extends the dependency-scoring strategies of
\inlinecite{roark06:sparseval} and
\inlinecite{owczarzak07evaluatingmt} using a widely-used and
publicly-available probabilistic context-free grammar (PCFG) parser and deterministic head-finding rules.

We may evaluate automatic MT measures in a variety of ways. Some
\cite{banerjee05meteor,liu05syntaxformteval,owczarzak07evaluatingmt}
have evaluated their success by comparing the measure to human
judgments of fluency and adequacy.  In other work, e.g.\
\inlinecite{snover06ter}, measures are evaluated by comparison to
human-targeted TER (HTER), a distance to a human-revised reference
that uses wording closer to the MT system choices (keeping the
original meaning) that is intended to measure the post-editing work
required after translation.  In this paper, we explore both kinds of
evaluation.

In section~\ref{sec:approach}, we outline our approach to including
syntactic information in MT evaluation, by describing a family of
metrics. In section~\ref{sec:paradigm}, we describe the implementation
details and make explicit which dimensions of this family of metrics
we explore in this paper.  Section~\ref{sec:faexpts} examines the
correlation of several members of this family with human judgments of
fluency and adequacy over a corpus of sentence translations and
selects a favorable member of the family, Expected Dependency Pair
Match (EDPM), based on this comparison. Section~\ref{sec:hter1}
compares the correlation of EDPM with HTER over a corpus of document-
and sentence-level comparisons, and demonstrates that its correlation
is favorable to that of competitor measures BLEU and TER at both
sentence and document levels, regardless of source-language or genre.
Section~\ref{sec:hter2} uses the tuning components of TERp
to explore the combination of these syntactic measures with TERp's
word-based measures. Finally, section~\ref{sec:conclusion} concludes
with some remarks on challenges and future work.

>>>>

A challenge in automatic machine translation (MT) evaluation is accounting
for allowable variability: two equally good
translations may be quite different in surface form. 
Currently, the most popular evaluation measures include a measure
based on $n$-gram precision known as BLEU \cite{papineni02bleu} and
the edit-distance measure Translation Edit Rate (TER)
\cite{snover06ter}.  These measures can only account for variability when 
given multiple translations, and studies show that they may
not accurately track translation quality both empirically
\cite{charniak03syntaxlmmt} and theoretically
\cite{callisonburch06bleuproblems}.

Alternative measures that 
incorporate synonym knowledge sources include: METEOR
\cite{banerjee05meteor}, which uses synonym tables and
morphological stemming to do progressively more forgiving matching;
%%MO: I am taking out the tuning stuff here since it isn't critical
%It can be tuned towards recall or precision, but is generally not
%tuned by users.  
TER Plus (TERp) \cite{snover09terp}, which is an extension of the
previously-mentioned TER that also incorporates synonym sets and stemming, along
with automatically-derived paraphrase tables.  
%TERp is explicitly
%intended to be tuned to a development set by users.
%
%Tuning has the advantage that the weight of different types of errors
%can be adjusted to match the needs of the task, though it makes it
%more difficult to compare results across tasks, particularly when
%there is little data for tuning.
Other metrics model syntactically-local (rather than string-local)
word-sequences include: tree-local
$n$-gram precision in various configurations of constituency and
dependency trees \cite{liu05syntaxformteval};\endnote{The dependency-based SParseval measure
\cite{roark06:sparseval}, designed as a parse-quality metric for
speech, is a similar approach, in that it is an F-measure over a
decomposition of reference and hypothesis trees.} and the \textbf{d} and
\textbf{d\_var} measures proposed by \inlinecite{owczarzak07evaluatingmt} that compare relational tuples derived from a
lexical functional grammar (LFG)
over reference and hypothesis translations.
%
These syntactically-oriented measures require a system for proposing
dependency structure over the reference and hypothesis
translations. \inlinecite{liu05syntaxformteval} use a
PCFG parser with deterministic head-finding, while 
\cite{owczarzak07evaluatingmt} extract the semantic dependency
relations from an LFG parser \cite{cahill04lfg}.
%
This work extends the dependency-scoring strategies of
\inlinecite{owczarzak07evaluatingmt}, which reported substantial
improvement in correlation with human judgment relative to BLEU and
TER, by using a 
publicly-available probabilistic context-free grammar (PCFG) parser and deterministic head-finding rules. In addition, we consider more types of constituents and different score combinations, as well as combination with of synonym-type scores.

MT measures are evaluated in a variety of ways. Some
\cite{banerjee05meteor,liu05syntaxformteval,owczarzak07evaluatingmt}
comparing the measure to human
judgments of fluency and adequacy.  In other work, e.g.\
\cite{snover06ter}, measures are compared to
human-targeted TER (HTER), a distance to a human-revised reference
that uses wording closer to the MT system choices (keeping the
original meaning) that is intended to measure the post-editing work
required after translation.  In this paper, we explore both kinds of
evaluation.

We describe our approach to including syntactic information in MT
evaluation by outlining a family of metrics in
section~\ref{sec:approach} and provide implementation details in
section~\ref{sec:paradigm}.  Section~\ref{sec:faexpts} examines the
correlation of several members of this family with human judgments of
fluency and adequacy, using the paradigm from
\cite{owczarzak07evaluatingmt} to provide comparisons to that work and
select a best case configuration, Expected Dependency Pair Match
(EDPM). The EDPM measure is then compared to BLEU and TER in terms of
correlation with HTER, exploring language/genre effects in
section~\ref{sec:hter1} and combination with TERp's synonym/paraphrase
features in section~\ref{sec:hter2}. Finally, findings and future work
are summarized in section~\ref{sec:conclusion}.
